
```{r setup, include = FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Static Plots

## Plot 1 (Numeric variable)

```{r}
nursing_summary |>
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = beds_10k), color = "black") + 
  labs(title = "Nursing Home Beds Available Nationwide",
       fill = "Beds Per\n10,000 People",
       caption = "Skilled Nursing Facility Cost Report (Data.CMS.gov)\n2020 Decennial Population Data (pewtrusts.org) ") +
  coord_map() +
  theme_void() +
  theme(legend.position = "bottom",
        plot.caption = element_text(hjust = 0),
                plot.title = element_text(face = "bold"),
                legend.title = element_text(face = "bold")) +
  scale_fill_viridis()  

favstats(~beds_10k, data = nursing_summary)
```

**Alt-Text:** This choropleth plot displays the 48 contiguous US states colored by the number of nursing home beds available per 10,000 people. The data ranges from about 21 to 101 beds per 10,000 people. The western half of the US has a relatively low number of beds, while the Midwest has more. Iowa has the greatest number of beds. The data were obtained from the [Skilled Nursing Facility Cost Report](https://data.cms.gov/provider-compliance/cost-report/skilled-nursing-facility-cost-report) and [2020 Decennial Population Data](https://www.pewtrusts.org/en/research-and-analysis/articles/2022/04/25/a-third-of-states-lost-population-in-2021).\
*SANILAC COUNTY MEDICAL CARE FACILITY of MI had 22,287 beds and was removed from the data for this analysis.*

## Plot 2 (categorical variable)

**Note: I created both my categorical variables from numerical variables in the data set because there weren't any appropriate existing variables.**

```{r}
nursing_summary |>
  ggplot(mapping = aes(x = long, y = lat, group = group)) + 
    geom_polygon(aes(fill = top_control_type), color = "black") + 
    coord_map() + 
    theme_void() +  
  theme(legend.position = "bottom",
        plot.caption = element_text(hjust = 0),
                plot.title = element_text(face = "bold"),
                legend.title = element_text(face = "bold")) +
  labs(title = "Most Common Type of Nursing Home Ownership",
       fill = "Type of Control",
       caption = "Data: Skilled Nursing Facility Cost Report (Data.CMS.gov)") +
    scale_fill_manual(values = c("#77AB43", "#008FD5", "#FF2700"))
```

**Alt-Text:** This choropleth plot displays the 48 contiguous US states colored by the most common type of ownership for nursing homes in the state. The three types of ownership are Nonprofit, Proprietary and Governmental. All of the states are dominated by Proprietary nursing homes except for four: North Dakota, South Dakota and Minnesota have more Nonprofit nursing homes than other types and Indiana has more Governmental nursing homes. The data were obtained from the [Skilled Nursing Facility Cost Report](https://data.cms.gov/provider-compliance/cost-report/skilled-nursing-facility-cost-report).
